\bf Excuse me, do you have a moment to talk about version control?

### 2017-07-07 README.Rmd
Edits and re-render

Why would a statistician use a version control system, such as [Git](http://git-scm.com) [@git]? And what is the point of hosting your work online, e.g., on [GitHub](https://github.com) [@github]? Could the gains possibly justify the inevitable pain?

@@

This has an implication for selecting your first Git projects: you will enjoy the most gain for your pain if you pick a project that involves sharing rapidly evolving files with others. It is tempting to pick a quiet, private project, but you risk missing out on the main benefits of formal version control.

@@

Statistics is an important part of Data Science, though there is lively debate about the exact relationship, both past and future [@donoho]. I strongly disagree with glib claims that "Data Science is just Statistics", which I've heard in academia. For reasons both genuine and pragmatic, Statistics departments want to participate in the growth of Data Science at their respective universities. So far, their success has been decidedly mixed [@donoho]. In the era of Data Science, staying current can't be limited to mathematical and methodological developments. The holistic work style described here is widely regarded as current best practice, yet we generally neither practice nor preach it in academic statistics. It is but one example of the many ways in which Data Science is **not** just statistics. By acknowledging the importance of modern workflows and tooling, Statistics can solidify its claim to being one of the core disciplines of Data Science.

>>>>

Why would a statistician use a version control system, such as [Git](https://git-scm.com) [@git]? And what is the point of hosting your work online, e.g., on [GitHub](https://github.com) [@github]? Could the gains possibly justify the inevitable pain?

@@

This has an implication for selecting your first Git projects: you will enjoy the most gain for your pain if you pick a project that involves sharing rapidly evolving files with others. It is tempting to pick a quiet, private project. But if you do, you may never find the benefits of formal version control compelling enough to cement the new habit.

@@

Statistics is an important part of Data Science, though there is lively debate about the exact relationship, both past and future [@donoho]. I strongly disagree with glib claims that "Data Science is just Statistics", which can be heard in academia. For reasons both genuine and pragmatic, Statistics departments want to participate in the growth of Data Science at their respective universities. So far, their success has been decidedly mixed [@donoho]. In the era of Data Science, staying current can't be limited to mathematical and methodological developments. The holistic work style described here is widely regarded as current best practice, yet we generally neither practice nor preach it in academic statistics. It is but one example of the many ways in which Data Science is **not** just statistics. By acknowledging the importance of modern workflows and tooling, Statistics can solidify its claim to being one of the core disciplines of Data Science.

### 2017-07-07 README.tex
Edits and re-render

Why would a statistician use a version control system, such as
\href{http://git-scm.com}{Git} \citep{git}? And what is the point of
hosting your work online, e.g., on \href{https://github.com}{GitHub}
\citep{github}? Could the gains possibly justify the inevitable pain?

@@

Statistics is an important part of Data Science, though there is lively
debate about the exact relationship, both past and future
\citep{donoho}. I strongly disagree with glib claims that ``Data Science
is just Statistics'', which I've heard in academia. For reasons both
genuine and pragmatic, Statistics departments want to participate in the
growth of Data Science at their respective universities. So far, their
success has been decidedly mixed \citep{donoho}. In the era of Data
Science, staying current can't be limited to mathematical and
methodological developments. The holistic work style described here is
widely regarded as current best practice, yet we generally neither
practice nor preach it in academic statistics. It is but one example of
the many ways in which Data Science is \textbf{not} just statistics. By
acknowledging the importance of modern workflows and tooling, Statistics
can solidify its claim to being one of the core disciplines of Data
Science.

>>>>

Why would a statistician use a version control system, such as
\href{https://git-scm.com}{Git} \citep{git}? And what is the point of
hosting your work online, e.g., on \href{https://github.com}{GitHub}
\citep{github}? Could the gains possibly justify the inevitable pain?

@@

Statistics is an important part of Data Science, though there is lively
debate about the exact relationship, both past and future
\citep{donoho}. I strongly disagree with glib claims that ``Data Science
is just Statistics'', which can be heard in academia. For reasons both
genuine and pragmatic, Statistics departments want to participate in the
growth of Data Science at their respective universities. So far, their
success has been decidedly mixed \citep{donoho}. In the era of Data
Science, staying current can't be limited to mathematical and
methodological developments. The holistic work style described here is
widely regarded as current best practice, yet we generally neither
practice nor preach it in academic statistics. It is but one example of
the many ways in which Data Science is \textbf{not} just statistics. By
acknowledging the importance of modern workflows and tooling, Statistics
can solidify its claim to being one of the core disciplines of Data
Science.
